Hierarchically modelling \emph{Kepler} dwarfs and subgiants to improve inference of stellar properties with asteroseismology

### 2021-02-04 paper/main.tex
changed '' to arcsec
Added serial comma

% Abstract of the paper <= 250 words
\begin{abstract}
    With recent advances in modelling stars using high-precision asteroseismology, the systematic effects associated with our assumptions of stellar helium abundance ($Y$) and the mixing-length theory parameter ($\mlt$) are becoming more important. We apply a new method to improve the inference of stellar parameters for a sample of \emph{Kepler} dwarfs and subgiants across a narrow mass range ($0.8 < M < \SI{1.2}{\solarmass}$). In this method, we include a statistical treatment of $Y$ and the $\mlt$. We develop a hierarchical Bayesian model to encode information about the distribution of $Y$ and $\mlt$ in the population, fitting a linear helium enrichment law including an intrinsic spread around this relation and normal distribution in $\mlt$. We test various levels of pooling parameters, with and without solar data as a calibrator. When including the Sun as a star, we find the gradient for the enrichment law, $\Delta Y / \Delta Z = 1.05\substack{+0.28\\-0.25}$ and the mean $\mlt$ in the population, $\mu_\alpha = 1.90\substack{+0.10\\-0.09}$. While accounting for the uncertainty in $Y$ and $\mlt$, we are still able to report statistical uncertainties of 2.5 per cent in mass, 1.2 per cent in radius, and 12 per cent in age. Our method can also be applied to larger samples which will lead to improved constraints on both the population level inference and the star-by-star fundamental parameters.% We show that more work is needed to study the validity of using the Sun as a calibrator for $Y$ and $\mlt$.
\end{abstract}

@@

The inference of stellar ages, masses and radii has improved through the use of asteroseismology in recent years \citep[e.g. see the review by][]{Chaplin.Miglio2013}. Measuring the oscillation modes in stars using photometric time series data, from missions such as \emph{CoRoT} \citep{Baglin.Auvergne.ea2006}, \emph{Kepler} \citep{Borucki.Koch.ea2010} and \emph{TESS} \citep{Ricker.Winn.ea2015} has given us new insights into the structure and evolution of stars \citep{Garcia.Ballot2019}. Recent examples include a deeper understanding of stellar structure \citep{Verma.Raodeo.ea2017}, chronology of a Milky Way merger \citep{Chaplin.Serenelli.ea2020} and classifying exoplanetary systems \citep{Huber.Chaplin.ea2019, Tayar.Claytor.ea2020}. Several studies used grids of stellar models with constraints from asteroseismology to produce catalogues of precise stellar parameters \citep{Pinsonneault.Elsworth.ea2014, SilvaAguirre.Lund.ea2017}. However, with increasing precision on fundamental parameters inferred from stellar models with asteroseismology, extra care should be taken to ensure that we are accounting for uncertainty in our choice of stellar physics.

@@

In this work, we apply the method of Davies et al. (in prep.) to determine stellar properties for a sample of \emph{Kepler} dwarfs and subgiants using a hierarchical Bayesian model (HBM). With an HBM, we introduce population-level distributions for $Y$ and $\mlt$ to encode prior information throughout the sample. We will show that when an HBM is used, we can increase the precision of inferred masses, radii and ages despite increasing the number of free parameters.

@@

To describe the distribution of $Y$ in this work, we assume a linear helium enrichment law characterised by freely varied population parameters: the gradient given by $\Delta Y / \Delta Z$, the primordial helium abundance at $Z=0$ ($Y_P$) and an intrinsic spread in helium ($\sigma_Y$). There have been many studies to determine a linear enrichment law, from modelling eclipsing binaries \citep{Ribas.Jordi.ea2000} to spectroscopy of galactic H\textsc{ii} regions \citep{Balser2006}. Values of $\Delta Y / \Delta Z$ have also been determined for samples of main sequence stars \citep{Casagrande.Flynn.ea2007}, open clusters \citep{Brogaard.VandenBerg.ea2012} and more recently with asteroseismology using individual oscillation frequencies \citep{SilvaAguirre.Lund.ea2017} and the glitch due to the second helium ionisation zone \citep{Verma.Raodeo.ea2019}. In these studies the value of the enrichment ratio was typically inferred to be $1 \lesssim \Delta Y / \Delta Z \lesssim 3$.

@@

For this study, we selected the sample of 415 stars from the first APOKASC catalogue of dwarfs and subgiants \citep[][hereafter \citetalias{Serenelli.Johnson.ea2017}]{Serenelli.Johnson.ea2017}. This sample provides an extensive set of dwarfs and subgiant stars with asteroseismic detections observed by the \emph{Kepler} mission. \citetalias{Serenelli.Johnson.ea2017} used grid-based modelling to determine the ages ($\tau$) masses ($M$) radii ($R$) and surface gravity ($\log g$) of stars in the sample, using global asteroseismic parameters, effective temperature ($\teff$) and metallicity ($\metallicity$) as inputs.

@@

To provide a means of calculating luminosities, we used \emph{Gaia} Data Release 2 (DR2) parallaxes \citep{GaiaCollaboration.Prusti.ea2016, GaiaCollaboration.Brown.ea2018}. We cross-matched the remaining sample with the DR2 catalogue, taking the nearest neighbours within a 4'' radius. Although DR2 parallaxes have improved upon the DR1 values at the time of \citetalias{Serenelli.Johnson.ea2017}, there was still evidence for a zero-point offset \citep{Lindegren.Hernandez.ea2018}. We adopted a global offset of \SI{0.05}{\milli\aarcsec}, in the sense that DR2 parallaxes were underestimated, representative of values obtained in the literature \citep[see e.g.][]{Riess.Casertano.ea2018, Zinn.Pinsonneault.ea2019, Hall.Davies.ea2019, Chan.Bovy2020}. We then cross-matched our sample with the Two-Micron All Sky Survey \citep[2MASS;][]{Skrutskie.Cutri.ea2006} to obtain \emph{K\textsubscript{S}}-band (\SI{2.16}{\micro\metre}) photometry.

% Return here to see if these two paragraphs may be merged.
We determined luminosities, $L$ for the sample using the direct method of \textsc{isoclassify} \citep{Huber.Zinn.ea2017, Berger.Huber.ea2020} with \emph{K\textsubscript{S}}-band photometry, \emph{Gaia} DR2 parallaxes, ASPCAP $\metallicity$ and $\teff$ and asteroseismic $\log g$ as inputs. This involved computing absolute \emph{K\textsubscript{S}}-band magnitudes using the \emph{Gaia} DR2 parallaxes and extinctions determined by the 3D galactic reddening maps of \citet{Green.Schlafly.ea2018}. We determined absolute bolometric magnitudes by interpolating the MIST bolometric correction tables as a function of $\teff$, $\log g$ and $\metallicity$ \citep{Dotter2016, Choi.Dotter.ea2016}. We adopted the uncertainty of \SI{0.02}{\magnitude} assumed by \textsc{isoclassify} for both the extinctions and bolometric corrections, corresponding to typical systematic errors in extinction maps and bolometric fluxes \citep[e.g.][]{Zinn.Pinsonneault.ea2019a,Tayar.Claytor.ea2020}. We obtained luminosities for the sample with a median uncertainty of 3.4 per cent.

The final sample comprised 81 stars for which we had complete data for $\teff$, $\metallicity$, $\dnu$ and $L$ to use as inputs for our stellar modelling method -- see Table \ref{tab:data}. In Figure \ref{fig:data}, we show the Hertzspring-Russell diagram for the sample plot in context with a series of stellar evolutionary tracks at solar metallicity.

@@

Firstly, we used a stellar evolutionary code to compute a grid of models to predict observable quantities (see Section \ref{sec:grid}). For a given mass ($M$), initial metallicity ($\metallicity_\mathrm{init}$), initial helium fraction ($Y_\mathrm{init}$) and mixing-length theory parameter ($\mlt$) our stellar models output $\teff$, $L$, radial oscillation modes and chemical composition as a function of age ($\tau$). Calls to models of stellar evolution are slow and the grid produced is discrete. This makes it difficult to robustly evaluate an HBM using the grid alone. We could interpolate the grid of stellar models. However, interpolation does not scale well with the number of input dimensions and points on the grid, reducing the scalability of our method.

@@

We trained the ANN using \textsc{TensorFlow} \citep{Abadi.Barham.ea2016}. We varied the architecture, number of batches, choice of loss function, optimizer and regularisation during the optimisation phase. For each set of ANN parameters, we initialised the ANN with a random set of weights and biases and minimized the loss over a given number of \emph{epochs}. An epoch is defined as one iteration through the entire training dataset, $\boldsymbol{\mathbb{D}}_\mathrm{train}$. We tracked the loss for each ANN using an independent validation dataset to determine the most effective choice of ANN parameters (see Section \ref{sec:opt}).

\subsubsection{Train, validation and test data}\label{sec:train}
%%%%%%%%%%%%%%%%%%%%%%%%
%%% TRAIN-TEST SPLIT %%%
%%%%%%%%%%%%%%%%%%%%%%%%

We built the train and validation datasets from the outputs of the grid of stellar models in Section \ref{sec:grid}. This included the input parameters: $M$, $\mlt$, $Y_\mathrm{init}$ and the initial heavy-elements fraction, $Z_\mathrm{init}$. We also included the $\teff$, $\log g$, $\dnu$, stellar age ($\tau$), radius ($R$), surface metallicity ($\metallicity_\mathrm{surf}$) and other chemical composition information generated by the models. We determined the fractional main sequence (MS) lifetime, $f_{\mathrm{MS}} = \tau / \tau_{\mathrm{MS}}$, of each evolutionary track by taking $\tau_{\mathrm{MS}}$ as the age when the central hydrogen fraction, $X_c < 0.01$. We then cut data where $f_{\mathrm{MS}} < 0.01$ to remove points on the grid prior to the MS. Once we had refined the data from the grid of models, we randomly sampled \num{7.736e6} points to use as the training dataset, with the remaining $\sim \num{2e6}$ points given to the validation dataset. We varied our choice of ANN input and output parameters among those available in the dataset during tuning (see Section \ref{sec:opt}).

% Additionally, we produced a test dataset of $\sim \num{2e6}$ stellar models evolved using \textsc{MESA}. Values for the initial $M$, $\metallicity$, $Y$ and $\mlt$ were chosen at the midpoint of the grid parameters described in Table \ref{tab:grid} such that they traced evolutionary tracks between those in the train and validation dataset. We prepared this dataset in the same way as the training set, but also constrained it to $\tau < \SI{15}{\giga\year}$ because we consider ages above $\sim \SI{15}{\giga\year}$ unphysical and such points are sparse in the training data. The test dataset was set aside and evaluated on the final ANN.
Additionally, we produced a test dataset of $\sim \num{2e6}$ stellar models evolved using \textsc{MESA}. Values for the initial $M$, $\metallicity$, $Y$ and $\mlt$ were chosen randomly within the range of grid parameters described in Table \ref{tab:grid} such that they spanned the breadth of the grid in an unbiased manner. We prepared this dataset in the same way as the training set, but also constrained it to $\tau < \SI{15}{\giga\year}$ because we consider ages above $\sim \SI{15}{\giga\year}$ unphysical and such points are sparse in the training data. The test dataset was set aside and evaluated on the final ANN.

@@

We trained an ANN to reproduce stellar observables according to our choice of physics with greater accuracy than typical observational precisions. We experimented with a variety of ANN parameter choices, such as the architecture, activation function, optimization algorithm and loss function. We tuned the ANN parameters by varying them in both a grid-based and heuristic approach, each time evaluating the accuracy using the validation dataset.

@@

We made predictions for each star using the trained ANN, $\{\log(\tau)_i, T_{\mathrm{eff}, i}, R_i, \dnu_i, \metallicity_{\mathrm{surf}, i}\} = \boldsymbol{f}_{\mathrm{ANN}}(\boldsymbol{\theta}_i)$, from which we derived the luminosity, $L_i$ using the Stefan-Boltzmann law. Out of the model parameters, those which may be observed are denoted by ${\boldsymbol{\mu}}_{i} = {\boldsymbol{f}}(\boldsymbol{\theta}_i)$. Therefore, we write the likelihood that we observe any $\boldsymbol{d}_i$ with known uncertainty, $\boldsymbol{\sigma}_{i}$ given our model as,
%
\begin{equation}
    p(\boldsymbol{d}_i | \boldsymbol{\theta}_i) = \prod_{k=1}^{N_\mathrm{obs}} \frac{1}{\sigma_{k, i} \sqrt{2\pi}} \exp\left[ - \frac{(d_{k, i} - \mu_{k, i})^2}{2 \sigma_{k, i}^2} \right],
    \label{eq:like}
\end{equation}
%
where $N_\mathrm{obs}$ is the number of observed variables. We chose to use observed $\teff$, $L$, $\dnu$ and $\metallicity$ collated for our sample as described in Section \ref{sec:data}.

@@

We constructed the PP model such that each of the initial helium, $\boldsymbol{Y}_\mathrm{init}$ and mixing-length theory parameter, $\boldsymbol{\alpha}_\mathrm{MLT}$ are drawn from a common distribution characterised by the set of hyperparameters, $\boldsymbol{\phi}$. Thus, Bayes' theorem becomes,
%
\begin{equation}
    p(\boldsymbol{\phi}, \boldsymbol{\Theta} | \boldsymbol{D}) \propto p(\boldsymbol{\phi}) \, p(\boldsymbol{Y}_\mathrm{init}, \boldsymbol{\alpha}_\mathrm{MLT} | \boldsymbol{\phi}) \, p(\boldsymbol{f}_{\mathrm{evol}}, \boldsymbol{M}, \boldsymbol{Z}) \, p(\boldsymbol{D} | \boldsymbol{\Theta}),
    \label{eq:hbmbayes}
\end{equation}
%
where $\boldsymbol{\Theta}$ is the same as in the NP model, i.e. each object-level parameter, $\boldsymbol{\theta}_j = \{\theta_{j, i}\}_{i=1}^{N_\mathrm{stars}}$, and $\boldsymbol{\phi} = \{\Delta Y/\Delta Z, Y_P, \sigma_Y, \mu_\alpha, \sigma_\alpha\}$. The hyperparameters for $\boldsymbol{Y}_\mathrm{init}$ comprise the helium enrichment ratio, ${\Delta Y}/{\Delta Z}$, primordial helium abundance fraction, $Y_P$ and the spread in helium, $\sigma_Y$. The remaining hyperparameters for $\boldsymbol{\alpha}_\mathrm{MLT}$ comprise the mean, $\mu_\alpha$ and spread, $\sigma_\alpha$.

@@

Similarly, for the second component of Equation \ref{eq:ppool}, we chose to partially-pool $\mlt$. We assume that convection in stars of a similar mass, evolutionary stage and area of the HR diagram may be approximated using a similar value of $\mlt$, but the accuracy of the mixing-length theory may vary from star-to-star. There is theoretical evidence for such a variation with $\metallicity$, $\teff$ and $\log{g}$ in 3D hydrodynamical stellar models \citep{Magic.Weiss.ea2015,Viani.Basu.ea2018}. However, investigating such dependencies are beyond this scope of this paper. Given the small range of our sample, any such variation will be absorbed by the spread parameter, $\sigma_\alpha$. Therefore, we decided to describe the prior on $\boldsymbol{\alpha}_\mathrm{MLT}$ as,
%
\begin{equation}
    p(\boldsymbol{\alpha}_{\mathrm{MLT}} | \mu_\alpha, \sigma_\alpha) = \prod_{i=1}^{N_\mathrm{stars}} \mathcal{N}({\alpha}_{\mathrm{MLT}, i} | \mu_\alpha, \sigma_\alpha).
\end{equation}
%

@@

Initially, we created a random synthetic population of stars using \textsc{MESA} to test the ability of the method to recover stellar properties according to our choice of model physics and population priors. We tested the NP, PP and MP models. Since our sample was fictitious, it would not have been appropriate to include real solar data. We summarise the results for the synthetic stellar parameters and hyperparameters in Appendix \ref{sec:test-stars}. We found that the models were able to recover the true synthetic properties accurately, with increased precision when pooling parameters.

@@

In this section, we present the results for each of the NP, PP and MP models with the sample of 81 APOKASC dwarfs and subgiants as inputs. We also present the results for the PPS and MPS models which include the Sun as a star in the population. Firstly, we show the reduction in age, mass and radius uncertainty with the addition of pooling in Section \ref{sec:param-results}. We then show the results for model hyperparameters in Section \ref{sec:hparam-results} where we infer the initial helium abundance and mixing-length parameter distribution in the sample.

@@

We obtained values for the hyperparameters for each of the models and present them in Table \ref{tab:hparam_results} along with their upper and lower 68 per cent credible regions. We omit the results for $Y_P$ because its posterior is the same as the prior, $Y_P=0.247\pm0.001$ for all the models. We fit the same hyperparameters from the PP model to the NP model results for $Y_\mathrm{init}$, $Z_\mathrm{init}$ and $\mlt$ for the purpose of comparison. However, the NP model results suffer from boundary effects which makes the resulting fit unreliable, pushing the population mean to the centre of the priors and underestimating the uncertainties. We leave the NP results here only for completeness.

@@

We assumed a linear helium enrichment law dependent only on the initial heavy element abundance, $Z_\mathrm{init}$. However, helium enrichment could vary non-linearly depending on other chemical abundances \citep{West.Heger2013} or the location of the star in the Milky Way \citep{Frebel2010}. Our model has the advantage of being adaptable to different population priors, stellar inputs and outputs. Future work will explore the helium enrichment relation further, with the inclusion of metal-poor stars and a dependence on different chemical abundances.

@@

Firstly, the results of \citetalias{Serenelli.Johnson.ea2017} were determined using stellar models calculated without heavy-element diffusion. The inclusion of diffusion when modelling the Sun has been commonplace over the last few decades, with good agreement between models and helioseismic observations \citep{Christensen-Dalsgaard.Proffitt.ea1993, Bahcall.Pinsonneault.ea1995}. More recent work explored the diffusion in cluster stars \citep{Korn.Grundahl.ea2007, Onehag.Gustafsson.ea2014} and another demonstrated the impact of including diffusion on stellar ages \citep{Dotter.Conroy.ea2017}. Our stellar models were computed with heavy-element diffusion. Recently, work by \citet{Nsamba.Campante.ea2018} on a similar sample of stars showed models without diffusion compared to those including diffusion can lead to, on average, underestimated radii and masses and overestimated ages by 1, 3 and 16 per cent respectively.

@@

\subsubsection{Mass, radius and age}

>>>>

% Abstract of the paper <= 250 words
\begin{abstract}
    With recent advances in modelling stars using high-precision asteroseismology, the systematic effects associated with our assumptions of stellar helium abundance ($Y$) and the mixing-length theory parameter ($\mlt$) are becoming more important. We apply a new method to improve the inference of stellar parameters for a sample of \emph{Kepler} dwarfs and subgiants across a narrow mass range ($0.8 < M < \SI{1.2}{\solarmass}$). In this method, we include a statistical treatment of $Y$ and the $\mlt$. We develop a hierarchical Bayesian model to encode information about the distribution of $Y$ and $\mlt$ in the population, fitting a linear helium enrichment law including an intrinsic spread around this relation and normal distribution in $\mlt$. We test various levels of pooling parameters, with and without solar data as a calibrator. When including the Sun as a star, we find the gradient for the enrichment law, $\Delta Y / \Delta Z = 1.05\substack{+0.28\\-0.25}$ and the mean $\mlt$ in the population, $\mu_\alpha = 1.90\substack{+0.10\\-0.09}$. While accounting for the uncertainty in $Y$ and $\mlt$, we are still able to report statistical uncertainties of 2.5 per cent in mass, 1.2 per cent in radius, and 12 per cent in age. Our method can also be applied to larger samples which will lead to improved constraints on both the population level inference and the star-by-star fundamental parameters.
\end{abstract}

@@

The inference of stellar ages, masses, and radii has improved through the use of asteroseismology in recent years \citep[e.g. see the review by][]{Chaplin.Miglio2013}. Measuring the oscillation modes in stars using photometric time series data, from missions such as \emph{CoRoT} \citep{Baglin.Auvergne.ea2006}, \emph{Kepler} \citep{Borucki.Koch.ea2010}, and \emph{TESS} \citep{Ricker.Winn.ea2015} has given us new insights into the structure and evolution of stars \citep{Garcia.Ballot2019}. Recent examples include a deeper understanding of stellar structure \citep{Verma.Raodeo.ea2017}, chronology of a Milky Way merger \citep{Chaplin.Serenelli.ea2020}, and classifying exoplanetary systems \citep{Huber.Chaplin.ea2019, Tayar.Claytor.ea2020}. Several studies used grids of stellar models with constraints from asteroseismology to produce catalogues of precise stellar parameters \citep{Pinsonneault.Elsworth.ea2014, SilvaAguirre.Lund.ea2017}. However, with increasing precision on fundamental parameters inferred from stellar models with asteroseismology, extra care should be taken to ensure that we are accounting for uncertainty in our choice of stellar physics.

@@

In this work, we apply the method of Davies et al. (in prep.) to determine stellar properties for a sample of \emph{Kepler} dwarfs and subgiants using a hierarchical Bayesian model (HBM). With an HBM, we introduce population-level distributions for $Y$ and $\mlt$ to encode prior information throughout the sample. We will show that when an HBM is used, we can increase the precision of inferred masses, radii, and ages despite increasing the number of free parameters.

@@

To describe the distribution of $Y$ in this work, we assume a linear helium enrichment law characterised by freely varied population parameters: the gradient given by $\Delta Y / \Delta Z$, the primordial helium abundance at $Z=0$ ($Y_P$) and an intrinsic spread in helium ($\sigma_Y$). There have been many studies to determine a linear enrichment law, from modelling eclipsing binaries \citep{Ribas.Jordi.ea2000} to spectroscopy of galactic H\textsc{ii} regions \citep{Balser2006}. Values of $\Delta Y / \Delta Z$ have also been determined for samples of main sequence stars \citep{Casagrande.Flynn.ea2007}, open clusters \citep{Brogaard.VandenBerg.ea2012}, and more recently with asteroseismology using individual oscillation frequencies \citep{SilvaAguirre.Lund.ea2017} and the glitch due to the second helium ionisation zone \citep{Verma.Raodeo.ea2019}. In these studies the value of the enrichment ratio was typically inferred to be $1 \lesssim \Delta Y / \Delta Z \lesssim 3$.

@@

For this study, we selected the sample of 415 stars from the first APOKASC catalogue of dwarfs and subgiants \citep[][hereafter \citetalias{Serenelli.Johnson.ea2017}]{Serenelli.Johnson.ea2017}. This sample provides an extensive set of dwarfs and subgiant stars with asteroseismic detections observed by the \emph{Kepler} mission. \citetalias{Serenelli.Johnson.ea2017} used grid-based modelling to determine the ages ($\tau$), masses ($M$), radii ($R$), and surface gravity ($\log g$) of stars in the sample, using global asteroseismic parameters, effective temperature ($\teff$), and metallicity ($\metallicity$) as inputs.

@@

To provide a means of calculating luminosities, we used \emph{Gaia} Data Release 2 (DR2) parallaxes \citep{GaiaCollaboration.Prusti.ea2016, GaiaCollaboration.Brown.ea2018}. We cross-matched the remaining sample with the DR2 catalogue, taking the nearest neighbours within a 4 arcsec radius. Although DR2 parallaxes have improved upon the DR1 values at the time of \citetalias{Serenelli.Johnson.ea2017}, there was still evidence for a zero-point offset \citep{Lindegren.Hernandez.ea2018}. We adopted a global offset of \SI{0.05}{\milli\aarcsec}, in the sense that DR2 parallaxes were underestimated, representative of values obtained in the literature \citep[see e.g.][]{Riess.Casertano.ea2018, Zinn.Pinsonneault.ea2019, Hall.Davies.ea2019, Chan.Bovy2020}. We then cross-matched our sample with the Two-Micron All Sky Survey \citep[2MASS;][]{Skrutskie.Cutri.ea2006} to obtain \emph{K\textsubscript{S}}-band (\SI{2.16}{\micro\metre}) photometry.

% Return here to see if these two paragraphs may be merged.
We determined luminosities, $L$ for the sample using the direct method of \textsc{isoclassify} \citep{Huber.Zinn.ea2017, Berger.Huber.ea2020} with \emph{K\textsubscript{S}}-band photometry, \emph{Gaia} DR2 parallaxes, ASPCAP $\metallicity$ and $\teff$, and asteroseismic $\log g$ as inputs. This involved computing absolute \emph{K\textsubscript{S}}-band magnitudes using the \emph{Gaia} DR2 parallaxes and extinctions determined by the 3D galactic reddening maps of \citet{Green.Schlafly.ea2018}. We determined absolute bolometric magnitudes by interpolating the MIST bolometric correction tables as a function of $\teff$, $\log g$ and $\metallicity$ \citep{Dotter2016, Choi.Dotter.ea2016}. We adopted the uncertainty of \SI{0.02}{\magnitude} assumed by \textsc{isoclassify} for both the extinctions and bolometric corrections, corresponding to typical systematic errors in extinction maps and bolometric fluxes \citep[e.g.][]{Zinn.Pinsonneault.ea2019a,Tayar.Claytor.ea2020}. We obtained luminosities for the sample with a median uncertainty of 3.4 per cent.

The final sample comprised 81 stars for which we had complete data for $\teff$, $\metallicity$, $\dnu$, and $L$ to use as inputs for our stellar modelling method -- see Table \ref{tab:data}. In Figure \ref{fig:data}, we show the Hertzspring-Russell diagram for the sample plot in context with a series of stellar evolutionary tracks at solar metallicity.

@@

Firstly, we used a stellar evolutionary code to compute a grid of models to predict observable quantities (see Section \ref{sec:grid}). For a given mass ($M$), initial metallicity ($\metallicity_\mathrm{init}$), initial helium fraction ($Y_\mathrm{init}$), and mixing-length theory parameter ($\mlt$) our stellar models output $\teff$, $L$, radial oscillation modes, and chemical composition as a function of age ($\tau$). Calls to models of stellar evolution are slow and the grid produced is discrete. This makes it difficult to robustly evaluate an HBM using the grid alone. We could interpolate the grid of stellar models. However, interpolation does not scale well with the number of input dimensions and points on the grid, reducing the scalability of our method.

@@

We trained the ANN using \textsc{TensorFlow} \citep{Abadi.Barham.ea2016}. We varied the architecture, number of batches, choice of loss function, optimizer, and regularisation during the optimisation phase. For each set of ANN parameters, we initialised the ANN with a random set of weights and biases and minimized the loss over a given number of \emph{epochs}. An epoch is defined as one iteration through the entire training dataset, $\boldsymbol{\mathbb{D}}_\mathrm{train}$. We tracked the loss for each ANN using an independent validation dataset to determine the most effective choice of ANN parameters (see Section \ref{sec:opt}).

\subsubsection{Train, validation, and test data}\label{sec:train}
%%%%%%%%%%%%%%%%%%%%%%%%
%%% TRAIN-TEST SPLIT %%%
%%%%%%%%%%%%%%%%%%%%%%%%

We built the train and validation datasets from the outputs of the grid of stellar models in Section \ref{sec:grid}. This included the input parameters: $M$, $\mlt$, $Y_\mathrm{init}$, and the initial heavy-elements fraction, $Z_\mathrm{init}$. We also included the $\teff$, $\log g$, $\dnu$, stellar age ($\tau$), radius ($R$), surface metallicity ($\metallicity_\mathrm{surf}$), and other chemical composition information generated by the models. We determined the fractional main sequence (MS) lifetime, $f_{\mathrm{MS}} = \tau / \tau_{\mathrm{MS}}$, of each evolutionary track by taking $\tau_{\mathrm{MS}}$ as the age when the central hydrogen fraction, $X_c < 0.01$. We then cut data where $f_{\mathrm{MS}} < 0.01$ to remove points on the grid prior to the MS. Once we had refined the data from the grid of models, we randomly sampled \num{7.736e6} points to use as the training dataset, with the remaining $\sim \num{2e6}$ points given to the validation dataset. We varied our choice of ANN input and output parameters among those available in the dataset during tuning (see Section \ref{sec:opt}).

% Additionally, we produced a test dataset of $\sim \num{2e6}$ stellar models evolved using \textsc{MESA}. Values for the initial $M$, $\metallicity$, $Y$ and $\mlt$ were chosen at the midpoint of the grid parameters described in Table \ref{tab:grid} such that they traced evolutionary tracks between those in the train and validation dataset. We prepared this dataset in the same way as the training set, but also constrained it to $\tau < \SI{15}{\giga\year}$ because we consider ages above $\sim \SI{15}{\giga\year}$ unphysical and such points are sparse in the training data. The test dataset was set aside and evaluated on the final ANN.
Additionally, we produced a test dataset of $\sim \num{2e6}$ stellar models evolved using \textsc{MESA}. Values for the initial $M$, $\metallicity$, $Y$, and $\mlt$ were chosen randomly within the range of grid parameters described in Table \ref{tab:grid} such that they spanned the breadth of the grid in an unbiased manner. We prepared this dataset in the same way as the training set, but also constrained it to $\tau < \SI{15}{\giga\year}$ because we consider ages above $\sim \SI{15}{\giga\year}$ unphysical and such points are sparse in the training data. The test dataset was set aside and evaluated on the final ANN.

@@

We trained an ANN to reproduce stellar observables according to our choice of physics with greater accuracy than typical observational precisions. We experimented with a variety of ANN parameter choices, such as the architecture, activation function, optimization algorithm, and loss function. We tuned the ANN parameters by varying them in both a grid-based and heuristic approach, each time evaluating the accuracy using the validation dataset.

@@

We made predictions for each star using the trained ANN, $\{\log(\tau)_i, T_{\mathrm{eff}, i}, R_i, \dnu_i, \metallicity_{\mathrm{surf}, i}\} = \boldsymbol{f}_{\mathrm{ANN}}(\boldsymbol{\theta}_i)$, from which we derived the luminosity, $L_i$ using the Stefan-Boltzmann law. Out of the model parameters, those which may be observed are denoted by ${\boldsymbol{\mu}}_{i} = {\boldsymbol{f}}(\boldsymbol{\theta}_i)$. Therefore, we write the likelihood that we observe any $\boldsymbol{d}_i$ with known uncertainty, $\boldsymbol{\sigma}_{i}$ given our model as,
%
\begin{equation}
    p(\boldsymbol{d}_i | \boldsymbol{\theta}_i) = \prod_{k=1}^{N_\mathrm{obs}} \frac{1}{\sigma_{k, i} \sqrt{2\pi}} \exp\left[ - \frac{(d_{k, i} - \mu_{k, i})^2}{2 \sigma_{k, i}^2} \right],
    \label{eq:like}
\end{equation}
%
where $N_\mathrm{obs}$ is the number of observed variables. We chose to use observed $\teff$, $L$, $\dnu$, and $\metallicity$ collated for our sample as described in Section \ref{sec:data}.

@@

We constructed the PP model such that each of the initial helium, $\boldsymbol{Y}_\mathrm{init}$ and mixing-length theory parameter, $\boldsymbol{\alpha}_\mathrm{MLT}$ are drawn from a common distribution characterised by the set of hyperparameters, $\boldsymbol{\phi}$. Thus, Bayes' theorem becomes,
%
\begin{equation}
    p(\boldsymbol{\phi}, \boldsymbol{\Theta} | \boldsymbol{D}) \propto p(\boldsymbol{\phi}) \, p(\boldsymbol{Y}_\mathrm{init}, \boldsymbol{\alpha}_\mathrm{MLT} | \boldsymbol{\phi}) \, p(\boldsymbol{f}_{\mathrm{evol}}, \boldsymbol{M}, \boldsymbol{Z}) \, p(\boldsymbol{D} | \boldsymbol{\Theta}),
    \label{eq:hbmbayes}
\end{equation}
%
where $\boldsymbol{\Theta}$ is the same as in the NP model, i.e. each object-level parameter, $\boldsymbol{\theta}_j = \{\theta_{j, i}\}_{i=1}^{N_\mathrm{stars}}$, and $\boldsymbol{\phi} = \{\Delta Y/\Delta Z, Y_P, \sigma_Y, \mu_\alpha, \sigma_\alpha\}$. The hyperparameters for $\boldsymbol{Y}_\mathrm{init}$ comprise the helium enrichment ratio (${\Delta Y}/{\Delta Z}$), primordial helium abundance fraction ($Y_P$), and the spread in helium ($\sigma_Y$). The remaining hyperparameters for $\boldsymbol{\alpha}_\mathrm{MLT}$ comprise the mean ($\mu_\alpha$) and spread, ($\sigma_\alpha$).

@@

Similarly, for the second component of Equation \ref{eq:ppool}, we chose to partially-pool $\mlt$. We assume that convection in stars of a similar mass, evolutionary stage and area of the HR diagram may be approximated using a similar value of $\mlt$, but the accuracy of the mixing-length theory may vary from star-to-star. There is theoretical evidence for such a variation with $\metallicity$, $\teff$, and $\log{g}$ in 3D hydrodynamical stellar models \citep{Magic.Weiss.ea2015,Viani.Basu.ea2018}. However, investigating such dependencies are beyond this scope of this paper. Given the small range of our sample, any such variation will be absorbed by the spread parameter, $\sigma_\alpha$. Therefore, we decided to describe the prior on $\boldsymbol{\alpha}_\mathrm{MLT}$ as,
%
\begin{equation}
    p(\boldsymbol{\alpha}_{\mathrm{MLT}} | \mu_\alpha, \sigma_\alpha) = \prod_{i=1}^{N_\mathrm{stars}} \mathcal{N}({\alpha}_{\mathrm{MLT}, i} | \mu_\alpha, \sigma_\alpha).
\end{equation}
%

@@

Initially, we created a random synthetic population of stars using \textsc{MESA} to test the ability of the method to recover stellar properties according to our choice of model physics and population priors. We tested the NP, PP, and MP models. Since our sample was fictitious, it would not have been appropriate to include real solar data. We summarise the results for the synthetic stellar parameters and hyperparameters in Appendix \ref{sec:test-stars}. We found that the models were able to recover the true synthetic properties accurately, with increased precision when pooling parameters.

@@

In this section, we present the results for each of the NP, PP, and MP models with the sample of 81 APOKASC dwarfs and subgiants as inputs. We also present the results for the PPS and MPS models which include the Sun as a star in the population. Firstly, we show the reduction in age, mass and radius uncertainty with the addition of pooling in Section \ref{sec:param-results}. We then show the results for model hyperparameters in Section \ref{sec:hparam-results} where we infer the initial helium abundance and mixing-length parameter distribution in the sample.

@@

We obtained values for the hyperparameters for each of the models and present them in Table \ref{tab:hparam_results} along with their upper and lower 68 per cent credible regions. We omit the results for $Y_P$ because its posterior is the same as the prior, $Y_P=0.247\pm0.001$ for all the models. We fit the same hyperparameters from the PP model to the NP model results for $Y_\mathrm{init}$, $Z_\mathrm{init}$, and $\mlt$ for the purpose of comparison. However, the NP model results suffer from boundary effects which makes the resulting fit unreliable, pushing the population mean to the centre of the priors and underestimating the uncertainties. We leave the NP results here only for completeness.

@@

We assumed a linear helium enrichment law dependent only on the initial heavy element abundance, $Z_\mathrm{init}$. However, helium enrichment could vary non-linearly depending on other chemical abundances \citep{West.Heger2013} or the location of the star in the Milky Way \citep{Frebel2010}. Our model has the advantage of being adaptable to different population priors, stellar inputs, and observables. Future work will explore the helium enrichment relation further, with the inclusion of metal-poor stars and a dependence on different chemical abundances.

@@

Firstly, the results of \citetalias{Serenelli.Johnson.ea2017} were determined using stellar models calculated without heavy-element diffusion. The inclusion of diffusion when modelling the Sun has been commonplace over the last few decades, with good agreement between models and helioseismic observations \citep{Christensen-Dalsgaard.Proffitt.ea1993, Bahcall.Pinsonneault.ea1995}. More recent work explored the diffusion in cluster stars \citep{Korn.Grundahl.ea2007, Onehag.Gustafsson.ea2014} and another demonstrated the impact of including diffusion on stellar ages \citep{Dotter.Conroy.ea2017}. Our stellar models were computed with heavy-element diffusion. Recently, work by \citet{Nsamba.Campante.ea2018} on a similar sample of stars showed, on average, models without diffusion compared to those including diffusion can lead to underestimated radii and masses, and overestimated ages by 1, 3, and 16 per cent respectively.

@@

\subsubsection{Mass, radius, and age}
